Methods for Large Scale Learning to Rank

### 2014-04-02 report/Chapters/BenchmarkResults.tex
werk tm vergaderring

With a meta-analysis I will compare the performance of Learning-to-Rank methods across the Learning-to-Rank benchmark datasets described in foregoing sections. With a literature review I will collect evaluation results on the datasets/collections. The following list presents an overview of the benchmark collections taken into account in the meta-analysis:
\begin{itemize}
\item LETOR 2.0
\item LETOR 3.0
\item LETOR 4.0
\item Yahoo! Learning to Rank Challenge
\item Yandex Internet Mathematics Competition 2009
\item MSLR-web10/30k
\item WCL2R
\item AOL
\end{itemize}

@@

>>>>

\subsection{Comparison methodology}
With a meta-analysis I will compare the performance of Learning-to-Rank methods across the Learning-to-Rank benchmark datasets described in foregoing sections. With a literature review I will collect evaluation results on the datasets/collections. The following list presents an overview of the benchmark collections taken into account in the meta-analysis:
\begin{itemize}
\item LETOR 2.0
\item LETOR 3.0
\item LETOR 4.0
\item Yahoo! Learning to Rank Challenge
\item Yandex Internet Mathematics Competition 2009
\item MSLR-web10/30k
\item WCL2R
\item AOL
\end{itemize}

@@

The LETOR 3.0 paper \cite{Qin2010} states that it may differ between datasets what the most accurate ranking methods are. To evaluate the overall performance of Learning-to-Rank methods over the multiple datasets in the LETOR 3.0 collections, Qin et al. \cite{Qin2010} proposed a measure called \emph{winning number} as the number of other algorithms that an algorithm can beat over the set of datasets. Formally the winning number measure is defined as

$S_i(M) = \sum\nolimits_{j=1}^n \sum\nolimits_{k=1}^m I_{\{M_i(j)>M_k(j)\}}$

where $j$ is the index of a dataset, $n$ the number of datasets in the comparison, $i$ and $k$ are indices of an algorithm, $M_i(j)$ is the performance of the $i$-th algorithm on the $j$-th dataset, $M$ is a ranking measure (such as \ac{nDCG} or \ac{MAP}), and $I_{\{M_i(j)>M_k(j)\}}$ is an indicator function such that

$I_{\{M_i(j)>M_k(j)\}} = \begin{cases}
1 \text{if} M_i(j) > M_k(k),
0 \text{otherwise}0
\end{cases}$
